---
title: "Understanding Italian Administrative Texts: A Reader-oriented Study for Text Readability and Simplification"
output: html_notebook
subtitle: "Error Analysis"
---

```{r}

library(tidyverse)
library(lme4)
library(car)
library(lmerTest)
library(effects)
library(interactions)
library(here)
library(jtools)
```
Load results of the tree subject groups and merge them in one dataframe.
```{r}
here()
control_path <- here("data", "results_control.csv")
control <- read.csv(control_path)
elderly_path <- here("data", "results_elderly.csv")
elderly <- read.csv(elderly_path)
l2_path <- here("data", "results_l2.csv")
l2 <- read.csv(l2_path)

test <- do.call("rbind", list(control, elderly, l2))
```
Set reference level on control group
```{r}
test$group <- as.factor(test$group)
test$group <- relevel(test$group,ref="control")
```
Scale and center readedu, admin, and digital index
```{r}
test <- mutate(test, readedu_centered = scale(readedu), admin_centered = scale(admin),
               digital_centered= scale(digital))
```
Compute the linear mixed model where the percetage of errors is function of complexity, group, readedu index, admin index, digital index (as fixed effects), user, and text (as random effects).
```{r}
lmm <- lmer(errors_perc ~ (complexity*group)*(readedu_centered+admin_centered+digital_centered) + (1|user) + (1|text), data = test)
summary(lmm)
```
Plot the three ways interaction between digital index, complexity and group.
```{r}
interact_plot(lmm,pred = digital_centered,modx = complexity,  mod2 = group, interval = TRUE,x.label = "Digital Literacy",y.label = "Error percentage",int.width = .95,mod2.labels = c("Control","Elderly","L2"))+theme_apa()
```
Set reference level on L2 group
```{r}
test$group <- as.factor(test$group)
test$group <- relevel(test$group,ref="L2")
```
Compute the linear mixed model where the percetage of errors is function of complexity, group, readedu index, admin index, digital index (as fixed effects), user, and text (as random effects).
```{r}
lmm <- lmer(errors_perc ~ (complexity*group)*(readedu_centered+admin_centered+digital_centered) + (1|user) + (1|text), data = test)
summary(lmm)
```
Plot the two ways interaction between admin index and group.
```{r}
interact_plot(lmm,pred = admin_centered,modx =group, interval = TRUE,x.label = "Admin Index",y.label = "Error percentage",int.width = .95,modx.labels = c('L2','Control','Elderly'))+theme_apa()
```

FOCUS ON L2
```{r}
l2_f_path <- here("data", "results_l2_focus.csv")
l2 <- read_csv(l2_f_path)
```
Scale and center certificate level, years in italy, years spent studying Italian, read, edu, readedu, admin, and digital index
```{r}
l2 <- mutate(l2, readedu_centered = scale(readedu), read_centered = scale(read),edu_centered = scale(edu), admin_centered = scale(admin),
             digital_centered= scale(digital),certificate_level_centered = scale(certificate_level), years_in_italy_centered = scale(years_in_italy),years_studying_italian_centered = scale(years_studying_italian))
```
Compute the linear mixed model where the percetage of errors is function of complexity, read index, edu index, admin index, digital index (as fixed effects), and user (as random effects).
```{r}
lmm <- lmer(errors_perc~ (complexity)*(edu_centered+read_centered+admin_centered+digital_centered+certificate_level_centered+years_in_italy_centered+years_studying_italian_centered) + (1|user) , data = l2)
summary(lmm)

```
Plot the two ways interaction between digital index and complexity.

```{r}
interact_plot(lmm,pred = digital_centered,modx = complexity,  interval = TRUE,x.label = "Digital Literacy",y.label = "Error percentage",int.width = .95,modx.labels = c('Complex','Simple'))+theme_apa()
```





