---
title: "Understanding Italian Administrative Texts: A Reader-oriented Study for Text Readability and Simplification"
output: html_notebook
subtitle: "Principal Component Analysis and Feature Analysis"
---

```{r}

library(tidyverse)
library(lme4)
library(car)
library(lmerTest)
library(effects)
library(interactions)
library(here)
library(jtools)
```
Load results of the tree subject groups and merge them in one dataframe.
```{r}
here()
control_path <- here("data", "results_control.csv")
control <- read.csv(control_path)
elderly_path <- here("data", "results_elderly.csv")
elderly <- read.csv(elderly_path)
l2_path <- here("data", "results_l2.csv")
l2 <- read.csv(l2_path)

test <- do.call("rbind", list(control, elderly, l2))

```
Compute the PCA on extracted features from each document 
```{r}
set.seed(114)
test.pca <- prcomp(test[15:27],center = T, scale = T, rank=3)
summary(test.pca)
```
Write PCA loading matrix on file
```{r}
out_pca_path <- here("data", "pca.csv")
write.csv(test.pca$rotation, out_pca_path)

```
Add PCA results on test dataframe
```{r}

test$PC1 <- test.pca$x[,1]
test$PC2 <- test.pca$x[,2]

```
Set reference level on control group
```{r}
test$group <- as.factor(test$group)
test$group <- relevel(test$group,ref="control")
```
Compute the linear mixed model where the percetage of errors is function of group, complexity, PC1,PC2 (as fixed effects), and user (as random effects).

```{r}
mod_filtered <- lmer(errors_perc ~ (group*complexity)*(PC1 + PC2 ) + (1|user), data = test)
summary(mod_filtered)
```
Set reference level on L2 group
```{r}
test$group <- as.factor(test$group)
test$group <- relevel(test$group,ref="L2")
```
Compute the linear mixed model where the percetage of errors is function of group, complexity, PC1,PC2 (as fixed effects), and user (as random effects).

```{r}
mod_filtered <- lmer(errors_perc ~ (group*complexity)*(PC1 + PC2) + (1|user) , data = test)
summary(mod_filtered)
```
Plot the three ways interaction between PC1, group and complexity.

```{r}
interact_plot(mod_filtered,pred = PC1,modx =group, mod2=complexity,interval = TRUE,x.label = "PC1 (Features related to morphology and sentence length)",y.label = "Error percentage",int.width = .95,mod2.labels = c('Complex','Simple'),modx.labels = c('L2','Control','Elderly'))+theme_apa()
```
Plot the main effect of PC1 on subject groups.

```{r}
interact_plot(mod_filtered,pred = PC2,modx =group, interval = TRUE,x.label = "PC2 (Features related to cohesion and morpho-syntax)",y.label = "Error percentage",int.width = .95, modx.labels = c('L2','Control','Elderly'))+theme_apa()
```

